Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-01-19 paper/main.tex
Remove email
Wrap lines to 80 characters

\author[1,*]{Charles Richter}
\author[2,3]{Hod Lipson}
\affil[1]{Cornell University, School of Mechanical and Aerospace Engineering, Ithaca, United States}
\affil[2]{Columbia University, Department of Mechanical Engineering, New York, United States}
\affil[3]{Columbia University, Data Science Institute, New York, United States}
\affil[*]{car45@cornell.edu}

@@

% % See https://tex.stackexchange.com/questions/286737/sub-figures-of-different-sizes-grid-layout
\begin{figure}%[!htb]
\centering
\begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[height=5cm]{figures/apparatus2}
    \caption{\label{fig:apparatus2}}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[height=5cm]{figures/apparatus3}
    \caption{\label{fig:apparatus3}}
\end{subfigure}
\caption{ \subref{fig:apparatus2} Front view of the flapping wing apparatus showing the wing mounted
  on its driving mechanism attached to the force sensor. \subref{fig:apparatus3} Close-up view of
  the 3D printed frame and crank mechanism used to drive the flapping motion of the wing.}
\end{figure}

\subsection*{High-speed measurement of flapping kinematics}
A Casio EXILIM EX-FH20 color video camera was used to record each experiment at
210 frames per second from a top-down perspective as well as a side view
provided by a mirror mounted in the field of view.  The main beam of each wing
was colored red to enable precise tracking of the stroke angle.  The top-down
projected area of the wing was used to extract deflection angle, and tracking
of the wing tip in the side-view was used to extract the angle of deviation out
of the wing's stroke plane.  These three angles precisely define the
configuration of the wing.  A schematic diagram of this apparatus is shown in
Figure~\ref{fig:apparatus}. A variety of image-processing techniques were used
to extract the kinematics of the wing motion from high-speed video.  The
red-colored main beam was identified with a color filter and a line was fitted
using a Hough Transform to identify the stroke angle.  The wing deflection
angle was computed by measuring the projected area of the wing in the image and
compared with the known dimensions of the rectangular wing shape. The
out-of-plane deviation angle of the wing was measured by tracking the leading
and trailing edge corners of the wingtip in the side-view of the mirror. We refer the reader to our
previous work for a more detailed description of our methods of extracting wing kinematics from
high speed video and processing the measured data\cite{richter2012thesis}.
% Figure~\ref{fig:kinematics} provides sample force data and measured wing kinematics from one
% experiment.

>>>>

\author[1]{Charles Richter} \author[2,3]{Hod Lipson} \affil[1]{Cornell
University, School of Mechanical and Aerospace Engineering, Ithaca, United
States} \affil[2]{Columbia University, Department of Mechanical Engineering, New
York, United States} \affil[3]{Columbia University, Data Science Institute, New
York, United States}

@@

% % See https://tex.stackexchange.com/questions/286737/sub-figures-of-different-sizes-grid-layout
\begin{figure}%[!htb]
\centering
\begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[height=5cm]{figures/apparatus2}
    \caption{\label{fig:apparatus2}}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[height=5cm]{figures/apparatus3}
    \caption{\label{fig:apparatus3}}
\end{subfigure}
\caption{\subref{fig:apparatus2} Front view of the flapping wing apparatus
  showing the wing mounted on its driving mechanism attached to the force
  sensor. \subref{fig:apparatus3} Close-up view of the 3D printed frame and
  crank mechanism used to drive the flapping motion of the wing.}
\end{figure}

\subsection*{High-speed measurement of flapping kinematics}
A Casio EXILIM EX-FH20 color video camera was used to record each experiment at
210 frames per second from a top-down perspective as well as a side view
provided by a mirror mounted in the field of view.  The main beam of each wing
was colored red to enable precise tracking of the stroke angle.  The top-down
projected area of the wing was used to extract deflection angle, and tracking of
the wing tip in the side-view was used to extract the angle of deviation out of
the wing's stroke plane.  These three angles precisely define the configuration
of the wing.  A schematic diagram of this apparatus is shown in
Figure~\ref{fig:apparatus}. A variety of image-processing techniques were used
to extract the kinematics of the wing motion from high-speed video.  The
red-colored main beam was identified with a color filter and a line was fitted
using a Hough Transform to identify the stroke angle.  The wing deflection angle
was computed by measuring the projected area of the wing in the image and
compared with the known dimensions of the rectangular wing shape. The
out-of-plane deviation angle of the wing was measured by tracking the leading
and trailing edge corners of the wingtip in the side-view of the mirror. We
refer the reader to our previous work for a more detailed description of our
methods of extracting wing kinematics from high speed video and processing the
measured data\cite{richter2012thesis}.
% Figure~\ref{fig:kinematics} provides sample force data and measured wing
% kinematics from one experiment.
